\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-25 doc/sui14/discussion.tex
created sui2014 dir
first pass with rebuttals

First, IR intensity measurements only work within the dynamic range of our sensor. Additional strong IR sources like direct sunlight may saturate the sensor and make discrimination impossible. Second, our adjacency map is built assuming stable relative target locations. If targets move, the map will have to be recalculated. This may be done incrementally during everyday interactions, but we have not yet tackled this challenge. We also have not yet evaluated how robust the adjacency map is when the user changes her location or view angle.

Finally, we acknowledge several limitations of our study design: we have not yet systematically studied target density variation, our study was performed in a lab environment, and only measured first use. We have also not investigated error rates in detail. Future work should study how the technique applies in realistic settings over longer periods of time.
%Point 3: Limitation
%Highlight the novelty of technique 2 & 3 while point out its weakness:
%- How sunlight will impact the techniques
%- Construct the adjacency mapping, what if objects move
%- How robust its adjacency mapping is when the user changes her location or view angle.
%- Outline programming by demonstration opportunities for future research
%- Study limitation: density variation, realistic settings, longitudinal studies to understand how users choose between our techniques and traditional list-based solution.

>>>>

First, IR intensity measurements only work within the dynamic range of our sensor. Additional strong IR sources like direct sunlight may saturate the sensor and make discrimination impossible. Second, our adjacency map is built assuming stable relative target locations. If targets move, the map will have to be recalculated. This may be done incrementally during everyday interactions, but we have not yet tackled this challenge.

Finally, we acknowledge several limitations of our study design: we have not yet systematically studied target density variation, our study was performed in a lab environment, and only measured first use. Future work should study how the technique applies in realistic settings over longer periods of time.
%Point 3: Limitation
%Highlight the novelty of technique 2 & 3 while point out its weakness:
%- How sunlight will impact the techniques
%- Construct the adjacency mapping, what if objects move
%- How robust its adjacency mapping is when the user changes her location or view angle.
%- Outline programming by demonstration opportunities for future research
%- Study limitation: density variation, realistic settings, longitudinal studies to understand how users choose between our techniques and traditional list-based solution.

\subsection{Computer-vision Solution?}
Reviewers suggest considering computer vision-based techniques with markers in the environment (such as QR codes, or Bokode [Mohan] which extends the working distance to a few meters for visual tags). We considered this direction and found several drawbacks, including computational complexity, low accuracy when targets are far, the absence of real-time environment feedback with passive tags, and aesthetic issues with QR codes. While we don't claim our choice of IR is optimal, it has important advantages -- it is low-cost, readily available and quite suitable for area selection. We can weaken our claim and add explanations of how disambiguation techniques might generalize to other methods of implementing target identification.

### 2014-06-25 doc/sui14/interaction.tex
created sui2014 dir
first pass with rebuttals

\subsection{Hardware}
A central hypothesis of this paper is that the area cursor paradigm~\cite{kabbash1995prince} is well matched to head orientation selection. Head orientation input is imprecise because it does not capture eye movement and has to rely on a low-bandwidth muscle group. Therefore, point selection techniques like laser pointers are not appropriate.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/interactionModel2.pdf}
\caption{Two main stages during the interaction with HOBS. For completeness, we have also show the final state of {\bf commit}.} 
\label{fig:interaction}
\end{figure}

>>>>

\subsection{Hardware}

\ben{a bit more on system description.}

A central hypothesis of this paper is that the area cursor paradigm~\cite{kabbash1995prince} is well matched to head orientation selection. Head orientation input is imprecise because it does not capture eye movement and has to rely on a low-bandwidth muscle group. Therefore, point selection techniques like laser pointers are not appropriate.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/interactionModel2.pdf}
\caption{{\em scan} and {\em refine} -- two main stages during the interaction with HOBS. For completeness, we have also added the final state of {\em commit}.} 
\label{fig:interaction}
\end{figure}

### 2014-06-25 doc/sui14/iteration2.tex
first pass with rebuttals

\subsection{Method}
To quantify the improvement in this design we performed a second study to compare the {\em Naive IR} and {\em Intensity IR} approaches. Because we were interested in discovering performance differences in denser environment, we reposition the 10 nodes and set them up in a smaller area (see Figure~\ref{fig:study-layout2}). We recruited 10 participants for this study. Each  user performed 30 target acquisition tasks for each approach. As in our first within-subject study, half of them perform {\em Naive IR} first and the other half {\em Intesity IR} first.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/study-layout2.pdf}
\caption{The environment setup for our second study. In comparison to our first study, we have delibrately increased the target density.}
\label{fig:study-layout2}
\end{figure}

@@

In the cases where disambiguation is inevitable, {\em Intensity IR} sorts the list based on the intensity reading, while {\em Naive IR} sorts alphabetically. {\em Intensity IR} reduces the fraction of refinement trails in which additional list navigation is necessary (i.e., the first, already selected element is incorrect).  {\em Intensity IR} sorted the desired target as the first one in the list in 55\% of cases (93 of 167). In comparison, for {\em Naive IR}, only 35\% of trials sorted the desired target as the first one in the list (80 out of 225). A Chi-square test show that this difference is significant (with $\chi^2(1) = 15.758$, $p < 0.0001$).

From Figure~\ref{fig:study2}, we can see that the overall target aquisition time has decreased from 4.31 seconds for {\em Naive IR} to 3.64 second for {\em Intensity IR}. This difference is also significant ($t(555)=3.2945$, $p=0.001$.)

>>>>

\subsection{Method}
To quantify the improvement in this design we performed a second study to compare the {\em Naive IR} and {\em Intensity IR} approaches. Because we were interested in discovering performance differences in denser environment, we reposition the 10 nodes and set them up in a smaller area (see Figure~\ref{fig:study-layout2}). We recruited 10 participants for this study. Each  user performed 30 target acquisition tasks for each approach. As in our first within-subject study, half of them perform {\em Naive IR} first and the other half {\em Intensity IR} first.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/study-layout2.pdf}
\caption{The environment setup for our second study. In comparison to our first study, we have deliberately increased the target density.}
\label{fig:study-layout2}
\end{figure}

@@

In the cases where disambiguation is inevitable, {\em Intensity IR} sorts the list based on the intensity reading, while {\em Naive IR} sorts alphabetically. {\em Intensity IR} reduces the fraction of refinement trails in which additional list navigation is necessary (i.e., the first, already selected element is incorrect).  {\em Intensity IR} sorted the desired target as the first one in the list in 55\% of cases (93 of 167) \ben{explicitly saying this is higher than random guess?}. In comparison, for {\em Naive IR}, only 35\% of trials sorted the desired target as the first one in the list (80 out of 225). A Chi-square test show that this difference is significant (with $\chi^2(1) = 15.758$, $p < 0.0001$).

From Figure~\ref{fig:study2}, we can see that the overall target acquisition time has decreased from 4.31 seconds for {\em Naive IR} to 3.64 second for {\em Intensity IR}. This difference is also significant ($t(555)=3.2945$, $p=0.001$.)

### 2014-06-25 doc/sui14/relatedwork.tex
first pass with rebuttals

>>>>

\ben{new related works from reviewers}.
\changes{RFIG Lamps and photosensing wireless tags [Raskar et al] use a projector and data is encoded in each pixel so that tags can localize themselves for target selection. Our IR emitter, a relatively low-cost solution, doesn’t have this feature but shares the commonality of covering an area for the ease of selection. At the end of their paper, they envision an IR-based system to solve ambient light problems. Our work lies in that direction and also contributes evaluations with user studies.
Progressive Refinement [Bacima] studies several progressive refinement selection modalities, which is close to our two-stage selection; but our contexts are head-orientation as it reflects users' point of interest.
}
